### 2015-04-15 draft.tex
..

We present a new iteration of the model where
\begin{enumerate}
  \item calls to our API does not expose the values of a packet's field, answering instead boolean queries about the values being in a certain range
  \item dynamic controllers are supported through a relation data-structure which is updated through an extended API
  \item the trace tree can be generated from executing the policy on a single (potentially symbolic) packet.
\end{enumerate}

% Including an example policy

\begin{figure}
\begin{lstlisting}
f(pkt):
  if RO.InRange(pkt, src, 0, 10) then
     RO.add(pkt, (dst, src), conn);
     fw(gateway)
  else if (RO.InSet(pkt, (src,dst), conn) then
         fw(dst)   
       else
         drop
       end
  end                
  \end{lstlisting}

@@

>>>>

To address these, we modify the model in the following way:
\begin{enumerate}
  \item calls to our API does not expose the values of a packet's field, answering instead boolean queries about the values being in a certain range
  \item dynamic controllers are supported through a relation data-structure which is updated through an extended API
  \item the trace tree can be generated from executing the policy on a single (potentially symbolic) packet.
\end{enumerate}

% Including an example policy, todo change 0 to 10 to actual IP
Figure~\ref{fig:firewall-eg} displays a policy for a stateful firewall using our API. Sources from 0 to 10 are taken to be internal to the network. If a packet is sent from an internal host to an external host, the pair of internal and external host is added to a list of trusted connection. If a packet is received from an external host, we lookup the table to see if the connection is trusted, in which case we forward the packet to its destination, otherwise we drop it.

\begin{figure}
\begin{lstlisting}
f(pkt):
  if RO.InRange(pkt, src, 0, 10) then
     if RO.InRange(pkt, dst, 0, 10) then
        RO.deliver()
     else 
        RO.add(pkt, (dst, src), trusted);
        RO.deliver()
  else if (RO.InSet(pkt, (src,dst), trusted) then
         RO.deliver()
       else
         RO.drop
       end
  end                
  \end{lstlisting}

@@

   \subsection*{Forwarding Decision}
   % can give constant decision (e.g. drop() or fwd(loc) to a certain location loc), or decision based on values of the packet (e.g. deliver() which forwards to dst)
